\SW: Crowd-sourcing the Discovery of Gravitational Lenses

### 2014-05-14 doc/sw-system.tex
Notes on Talk, QD

For the more interesting subjects, the CI offers two features that  enable
further investigation of the subjects. First is the ``Quick Dashboard,'' a
more advanced image viewer. This allows the viewer to compare three different
contrast and color balance settings, to help bring out subtle features, and to
zoom in on interesting regions of the image to assess small features. Markers
can be placed in the Quick Dashboard just the same as in the main CI image
viewer. The second is a link to that subject's page in the project discussion
forum, \texttt{http://talk.spacewarps.org}. Here, volunteers can discuss the
features they have seen either before they submit their classification, or
after, if they ``favorite'' the subject. There is no ``back'' button, however:
each volunteer may only classify a given subject once.

>>>>

For the more interesting subjects, the CI offers two features that  enable
further investigation of the subjects. First is the ``Quick Dashboard,'' a
more advanced image viewer. This allows the viewer to compare three different
contrast and color balance settings, to help bring out subtle features, and to
zoom in on interesting regions of the image to assess small features. Markers
can be placed in the Quick Dashboard just the same as in the main CI image
viewer. The second is a link to that subject's page in the project discussion
forum, \texttt{http://talk.spacewarps.org}. Here, volunteers can discuss the
features they have seen either before they submit their classification, or
after, if they ``favorite'' the subject. There is no ``back'' button: each
volunteer may only classify a given subject once. However, the presence of an
option to see what others think about any given subject before submitting your
own classification means that the classifications may not be  strictly
independent; the advantage of this system is that volunteers can learn from
others what constitutes a good lens candidate. In practice, we might expect
this to be a relatively unimportant educational resource, given the explicit
training we provide for the volunteers, which we describe in the next section.
